Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-25 paper/paper.tex
Fix typo.
small changes

Fig. \ref{fig:RetingDist} shows density plots of rating pairs, for $N \geq 40$
and $N \geq 80$. These data, together with the similarity score histograms of Fig.
\ref{fig:Histograms}, suggest that the data for our two data sets are similar
and that large biases are not introduced by varying the number of common users,
$N$. At the same time, both rating distributions reveal significant correlations
between Rating1 and Rating2 as evidenced by the elongation in the $45^\circ$
direction. This is consistent with the data of Fig. \ref{fig:Histograms}, which
shows the mean $PearSim > 0$ for both sets. Further, these data indicate a
bias toward positive values among rating pairs compared to those of ratings in
general, which have an average value of zero by construction\footnote{See
discussion of bias subtraction in {\bf Data} section.}. This latter feature
indicates that items with large numbers of common users tend to be rated higher
by their common users than by their other users since we have already subtracted
the item's average rating thereby avoiding any simple popularity effects.

We observe that while the data of Fig. \ref{fig:RatingDist} clearly do not
conform precisely to a multivariate Gaussian distribution, this approximation is
not an unreasonable one. In passing, we remark on the faint clusters that flank
the central cluster in the figures. We understand these to be artifacts of the
bias subtraction. Moreover, a more sophisticated Rating-based model could
account for these by considering a $P(\vec{R} | Y)$ that is a mixture of
Gaussians.

>>>>

Figure \ref{fig:RatingDist} shows density plots of rating pairs, for $N \geq 40$
and $N \geq 80$. These data, together with the similarity score histograms of Fig.
\ref{fig:Histograms}, suggest that the data for our two data sets are similar
and that large biases are not introduced by varying the number of common users,
$N$. At the same time, both rating distributions reveal significant correlations
between Rating1 and Rating2 as evidenced by the elongation in the $45^\circ$
direction. This is consistent with the data of Fig. \ref{fig:Histograms}, which
shows the mean $PearSim > 0$ for both sets. Further, these data indicate a
bias toward positive values among rating pairs compared to those of ratings in
general, which have an average value of zero by construction\footnote{See
discussion of bias subtraction in {\bf Data} section.}. This latter feature
indicates that items with large numbers of common users tend to be rated higher
by their common users than by their other users since we have already subtracted
the item's average rating thereby avoiding any simple popularity effects.

We observe that while the data of Fig. \ref{fig:RatingDist} do not
conform precisely to a multivariate Gaussian distribution, this approximation is
not an unreasonable one. In passing, we remark on the faint clusters that flank
the central cluster in the figures. We understand these to be artifacts of the
bias subtraction. Moreover, a more sophisticated Rating-based model could
account for these by considering a $P(\vec{R} | Y)$ that is a mixture of
Gaussians.
